Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-01-28 content.tex
Describe DD model, fix #79

We show the usage of \verb;pirouette; by gradually introducing
its features.
First, to get an idea of the baseline error, 
we measure the Bayesian inference error when we start from a phylogeny 
generated under a known and standard tree model.
Second, to establish that the true tree prior is indeed the best, 
we also measure the inference error made by a
best candidate inference model.
Lastly, we quantify the impact of the tree prior in the Bayesian inference. 
We do so by separating the baseline error from the complete error 
running the pipeline starting from a tree generated by an unknown 
or non-standard tree model.

@@

So far we have measured the inference error on a tree
generated according to a known (and standard) tree diversification model. 
The goal of \verb;pirouette; is to measure the expected impact of a novel tree prior.
To do so, in this example, we will use a tree generated by a non-standard 
tree diversification model, assumed to be closely related to the Yule tree prior.
We measure both the baseline 
error (that serves as a control) and the full inference error, because their 
difference shows the impact of the tree model.
We obtain the baseline error by using a twin tree (see Subsection~\ref{subsec:twinning}) for 
both the generative and best candidate models.
The research question this example answers is:
"What is the inference error made from a phylogeny, 
for both a generative model and the best candidate model?"

We start from the tree generated by a non-standard (and unknown) diversification model, 
having six taxa and a crown age of ten:
\begin{lstlisting}[
  language = R, 
  floatplacement = ht,
  frame = single, 
  label = {lst:unknown_phylogeny},
  caption = A phylogeny generated by an unknown diversification model.
]
phylogeny  <- ape::read.tree(
  text = "(((A:8, B:8):1, C:9):1, ((D:8, E:8):1, F:9):1);"
)
\end{lstlisting}
\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_3/example_3_314/true_tree.png}
  \caption{The tree derived from an unknown diversification process, 
    as created by listing~\ref{lst:unknown_phylogeny}.
    The scale overlaps with the lower branch, which is the default 
    behavior for the plotting function used.
  }
\end{figure}

>>>>

We show the usage of \verb;pirouette; by gradually introducing
its features.
First, to get an idea of the baseline error, 
we measure the Bayesian inference error when we start from a phylogeny 
generated under a known and standard tree model.
Second, to establish that the true tree prior is indeed the best, 
we also measure the inference error made by a
best candidate inference model.
Lastly, we quantify the impact of the tree prior in the Bayesian inference. 
We do so by separating the baseline error from the complete error 
running the pipeline starting from a tree generated by a non-standard tree model.

@@

So far we have measured the inference error on a tree
generated according to a known (and standard) tree diversification model. 
The goal of \verb;pirouette; is to measure the expected impact of a novel tree prior.
To do so, in this example, we will use a tree generated by a non-standard 
tree diversification model, assumed to be closely related to the Yule tree prior.
We'll use the diversity-dependent tree model \cite{etienne2011diversity},
which is a birth-death model with a speciation that is dependent on the
number of species.
We measure both the baseline 
error (that serves as a control) and the full inference error, because their 
difference shows the impact of the tree model.
We obtain the baseline error by using a twin tree (see Subsection~\ref{subsec:twinning}) for 
both the generative and best candidate models.
The research question this example answers is:
"What is the inference error made from a phylogeny, 
for both a generative model and the best candidate model?"

We start from the tree generated by a diversity-dependent model,
having six taxa and a crown age of ten:
\begin{lstlisting}[
  language = R, 
  floatplacement = ht,
  frame = single, 
  label = {lst:unknown_phylogeny},
  caption = A phylogeny generated by an unknown diversification model.
]
# NEW CODE HERE, 
# depends on https://github.com/richelbilderbeek/pirouette_article/issues/75
#
# phylogeny  <- ape::read.tree(
#   text = "(((A:8, B:8):1, C:9):1, ((D:8, E:8):1, F:9):1);"
# )
\end{lstlisting}
\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_3/example_3_314/true_tree.png}
  \caption{The tree derived from an unknown diversification process, 
    as created by listing~\ref{lst:unknown_phylogeny}.
    The scale overlaps with the lower branch, which is the default 
    behavior for the plotting function used.
  }
\end{figure}
